### 2021-08-04 paper/paper.tex
update TODO notes

\todo{TODO: Be careful how to formulate this, be neutral and avoid making people angry} %TODO

@@

\todo{ % TODO
\begin{itemize}
  \item Full paper: 5--10 pages
  \item Prepare repro repo including scripts for \trixi and FLUXO
  \item Restructure non-conservative stuff and add MHD benchmarks
  \item Shall we re-create the schematic overview in tikz?
  \item Shall we compare \trixi (in terms of structure, not performance!)
        to other open source frameworks such as MFEM,
        NGSolve, DealII, DUNE, FENICS, Firedrake, ClawPack, ...? Definitely not
        explicitly to not make people angry, but maybe implicitly without
        mentioning their names?
        \begin{itemize}
          \item Gregor will think about it!
        \end{itemize}
  \item Are there other aspects we should discuss?
  \item Check affiliations
  \item Check order of authors
  \item Maybe include some cool pictures? Give a flavor of the kind of simulations
        you can do with \trixi? Pictures trigger people! For example after the
        list of main features?
  \item A simple example where we really use multiple dispatch?
        \begin{itemize}
          \item Just pass functions around
          \item Dispatch on parameters of DG struct
        \end{itemize}
\end{itemize}
\begin{quote}
  Compared to an extended abstract, a full paper presents more of the background
  and context motivating the work. It compares the work to other approaches taken
  in the field and gives some additional insights on the conference contribution.
  Use cases back up the work by showing how it can be used.
\end{quote}}

>>>>

\todo{TODO: Gregor. Be careful how to formulate this, be neutral and avoid making people angry} %TODO: Gregor

@@

\todo{ % TODO
\begin{itemize}
  \item Full paper: 5--10 pages
  \item Prepare repro repo including scripts for \trixi and FLUXO
  \item Rerun Euler benchmarks and add MHD benchmarks
  \item Shall we re-create the schematic overview in tikz?
  \item Gregor: Other aspects of other codes that we like more in \trixi?
  \item Are there other aspects we should discuss?
  \item Check affiliations
\end{itemize}
\begin{quote}
  Compared to an extended abstract, a full paper presents more of the background
  and context motivating the work. It compares the work to other approaches taken
  in the field and gives some additional insights on the conference contribution.
  Use cases back up the work by showing how it can be used.
\end{quote}}
